%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Add various styling and section options and allow for multiple pages smoothly.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.3:
% 1. Removed MacFonts version as I have no desire to maintain it nor access to macOS
% 2. Switched column ordering
% 3. Changed font styles/colors for easier human readability
% 4. Added, removed, and rearranged sections to reflect my own experience
% 5. Hid last updated
%
% v1.2:
% 1. Added publications in place of societies.
% 2. Collapsed a portion of education.
% 3. Fixed a bug with alignment of overflowing long last updated dates on the top right.
%
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{\href{https://github.com/sunnydodti}{Sunny Dodti}}{
\faGlobe \hspace{0.1em} \href{https://github.com/sunnydodti}{Portfolio} \hspace{0.5em} | \hspace{0.5em}
\faGithub \hspace{0.1em} \href{https://github.com/sunnydodti}{GitHub} \hspace{0.5em} | \hspace{0.5em}
\faLinkedin \hspace{0.1em} \href{https://www.linkedin.com/in/sunnydodti/}{LinkedIn} \hspace{0.5em} | \hspace{0.5em}
\faEnvelope \hspace{0.1em} \href{mailto:sunnydodti+resume@gmail.com}{sunnydodti+career@gmail.com} \hspace{0.5em} | \hspace{0.5em}
\faPhone \hspace{0.1em} \href{tel:9607782965}{+91 9607782965}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Software Engineer}
\descript{| \hspace{0.1em}  Xoriant (Client AWS) }
\location{Aug 2023 – Present | Mumbai, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Delivered key features ahead of schedule, earning client appreciation.
\item Transitioned to Serverless, cutting infrastructure costs by 40\%.
\item Secured role-based authentication for 20K+ users via AWS Cognito.
\item Improved document retrieval speed by 40\% in .NET applications.
\item Migrated legacy applications to .Net 8, reducing maintenance costs by 30\%.
\item Developed and maintained Nuget Package Libraries.
\item Created 1000+ unit tests, reducing bugs by 35\%.
\item Automated CI/CD pipelines, cutting deployment time from 1 hour to 15 minutes.

\end{tightemize}
\sectionsep

\runsubsection{Associate Software Engineer}  
\descript{| \hspace{0.1em} Xoriant }
\location{Aug 2022 – Aug 2023 | Mumbai, IN}
\begin{tightemize}
\item Developed an AI-driven system for intelligent document processing and question-answering on extracted data.
\item Created a async pipeline for data extraction and processing using Azure Form Recognizer, AWS Textract \& Gen AI.
\item Real time Chat bot for answering questions on extracted data using Bedrock and OpenAI.
\item Built a React frontend with user-friendly interface and seamless user experience.
\item Designed a scalable Django REST Framework (DRF) backend with SQLite for efficient data storage and retrieval.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Expense Tracker}
\descript{| \hspace{0.1em} App | Web | Flutter | 
\href{https://expense-tracker.persist.site}{\faExternalLink }
}
\location{Jan 2024 – Present}
\begin{tightemize}

\item AI-powered personal finance management app 
\item Data visualization \& Smart Alerts.
\item Bill scanning \& automation for repeating expenses. 
\item Budget planning and multi-profile expense management.
\end{tightemize}
\sectionsep

\runsubsection{Url Shortner}
\descript{| \hspace{0.1em} App | Web | Flutter | \href{https://github.com/sunnydodti/url-shortner}{\faGithub } | 
\href{https://urls.persist.site}{\faExternalLink }
} 
\location{Mar 2024 – Mar 2024}
\begin{tightemize}
\item A simple Url Shortner
\end{tightemize}

\sectionsep

\runsubsection{Authenticator}
\descript{| \hspace{0.1em} App | Web | Flutter | \href{https://github.com/sunnydodti/authenticator}{\faGithub } | 
\href{https://authenticator.persist.site}{\faExternalLink }
} 
\location{Dec 2024 – Jan 2024}
\begin{tightemize}
\item Secure 2FA mobile app built with Flutter and SQLite.
\item TOTP authentication implementation
\item QR code scanning \& secure token storage
\item Flutter, SQLite, Provider pattern
\item Folders for grouping accounts
\end{tightemize}

\sectionsep

\runsubsection{Other Projects}
\begin{tightemize}
\item \textbf{PearPin - A Password Generator} 
| \href{https://github.com/sunnydodti/pearpin}{\faGithub}
| \href{https://pearpin.persist.site}{\faExternalLink}

\item \textbf{KiwiCLock - A Cloud Timer} 
| \href{https://github.com/sunnydodti/kiwiclock}{\faGithub}
| \href{https://kiwiclock.persist.site}{\faExternalLink}

\item \textbf{Currency Converter} 
| \href{https://github.com/sunnydodti/currency_converter}{\faGithub}
| \href{https://sunnydodti.github.io/currency_converter}{\faExternalLink}

\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Bachelor of Engineering}
\descript{University of Mumbai}
\descript{Computer Engineering}
\location{2022 | Mumbai, India}
\sectionsep

\subsection{Diploma}
\descript{Computer Technology}
\location{2019 | Vasai, India} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Technology}
.Net 8  \textbullet Flutter \textbullet ReactJS \textbullet SpringBoot \\
Supabase \textbullet Firebase  \\
Mobile Applications
\sectionsep

\subsection{AWS}
Bedrock \textbullet Textract \\
Lambda \textbullet EC2 \textbullet Cognito \\
S3 \textbullet EBS \textbullet EFS\\
SQS \textbullet SNS \\
RDS \textbullet Aurora \\
ELB \textbullet ASG \\
IAM \\
\sectionsep

\subsection{Others}
Git \textbullet Figma \\
NewRelic \textbullet SonarQube \\
\sectionsep

\subsection{Database}
SQLite \textbullet PostgreSQL \\
SQL Server \textbullet MySQL \\
\sectionsep

\subsection{Programming Languages}
Python \textbullet{} C\# \textbullet{} Dart \\
JavaScript \textbullet{} Java \\
Bash
\sectionsep

\subsection{Languages}
English \textbullet{} Hindi \textbullet{} Marathi \\
Korean (Learning) 
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}